HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-07-25 scnn.tex
work in section 4

Forunately, both of these computational issues can be overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parameterized by $K+1$ coefficients $\theta$. In that specific case, the filtering operation \eqnref{graph_convolution} becomes
\begin{equation} \label{eqn:graph_convolution_polynomial}
	h_\theta(\L) \f =  \U \left(\sum_{k=0}^K \theta_k \bLambda^k \right) \U\trans \f = \sum_{k=0}^K \theta_k \L^k \f,
\end{equation}
an operation requiring $k$ multiplication of the graph Laplacian matrix $\L$. In our case, the Laplacian is extremly sparse ($8-9$ entries per line), making the filtering operation for a fixed $k$ linear in the number of pixel $N_{pix}$.
Here happens the transition from filtering in the spectral domain to filtering in the vertex domain. Note that $\L^k$ captures $k$-neighborhoods, i.e., $(\L^k)_{ij}$ is non-zero if and only if nodes $v_i$ and $v_j$ are connected by a path of length $k$. As such, filtering with a polynomial convolution kernel can be interpreted in the vertex domain as a local weighted linear combination of the signal's value. The weights are determined by the filter coefficients $\theta$ and the path weight, defined as the multiplication of all edge weights along the path.
\todo{Better vertex domain explanation.}

>>>>

Forunately, both of these computational issues can be overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parameterized by $K+1$ coefficients $\theta$. In that specific case, the filtering operation \eqnref{graph_convolution} becomes
\begin{equation} \label{eqn:graph_convolution_polynomial}
	h_\theta(\L) \f =  \U \left(\sum_{k=0}^K \theta_k \bLambda^k \right) \U\trans \f = \sum_{k=0}^K \theta_k \L^k \f,
\end{equation}
an operation requiring $k$ multiplication of the graph Laplacian matrix $\L$. In our case, the Laplacian is extremly sparse ($8-9$ entries per line), making the filtering operation for a fixed $k$ linear in the number of pixel $N_{pix}$.
Moreover, here happens the transition from filtering in the spectral domain to filtering in the vertex domain. The matrix $\L^k$ captures $k$-neighborhoods of each pixel, i.e., $(\L^k)_{ij}$ is non-zero if and only if nodes $v_i$ and $v_j$ are connected by a path of length $k$. 
As such, filtering with a polynomial convolution kernel can be interpreted in the pixel (vertex) domain as a weighted linear combination of the pixels neighboors values. The weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$.
\todo{Better vertex domain explanation. \nati{I gave it a try}}
